Pattern matching for (231,213) avoiding permutations

### 2015-01-29 article.tex
corrections of typo

% le set avoid 231,213
\newcommand{\C}[1]{A_{#1}(231,213)}

@@

\title{Pattern matching for (231,231) avoiding permutations}
\author{Both Emerite NEOU, Romeo RIZZI}
\date{}

@@

	\abstract{
	  	Given two permutations, 
	  	a text $\ptext$ 
	  	and a motif $\pmotif$,
	  	the \textbf{permutation pattern problem}
	  	asks if there exists a normalized subsequence of $\ptext$
	  	which equals $\pmotif$.
	  	We study this problem for the permutation 
	  	avoiding (231,231).

	}

@@

		We denote by $A_{n}(m_1,m_2)$ the class
		of permutation of size $n$ which avoid 
		the motif $m_1$ and $m_2$. 
		$\Perm{n}$ the permutation of size $n$.
		$[n]$ the set $\{1,2,...,n\}.$
		For a permutation p, let $p[i:j]$, 
		be the permutation from element $i$ to $j$,
		$p[:j]$ be the prefix ending at index $j$
		and $p[i:]$ be the suffix starting at index $i$.\\

		Given two permutations
		$\pmotif$ and $\ptext$
		we say that $\pmotif$
		is a motif/match of
		$\ptext$,
		if and only if
		there exists 
		and increasing function 
		$\sigma:[|\pmotif|]->[|\pmotif|]$
		such that : $\forall i$ and 
		$\forall j$ $i,j \in |\pmotif| $
		if $\pmotif(i)<\pmotif(j)$
		then $\ptext(\sigma(i))<\ptext(\sigma(j))$.\\

@@

		A \textbf{Stripe} of a permutation
		 is a mapping into \textbf{up step} (noted $\ustep$) 
		or a \textbf{down step} (noted $\dstep$).
		An element $i$ of a permutation $p$ is an up step if and only if $i$ is not the last element and $p(i)<p(i+1)$.
		An element $i$ of a permutation $p$ is a down step if and only if $i$ is not the last element and $p(i)>p(i+1)$.	
		By convention the last element is mapped as the second to last element.\\ 	
		Formally a Stripe is a function $\mathcal{S} : \Perm{n},[n] \to \{\dstep,\ustep\}$ define as :\\
		$ \mathcal{S}(p,i) = \left\{ 
		  \begin{array}{l l}
		    \ustep & \quad \text{if $1 \leq i<n$ and $p(i+1)-p(i)>0$ }\\
		    \dstep & \quad \text{if $1 \leq i<n$ and $p(i+1)-p(i)<0$ }\\
		     \mathcal{S}(p,n-1) & \quad \text{if $i=n$}\\
		  \end{array} \right. $\\

@@

		Formally we say that the stripe of $\pmotif \in \Perm{m}$ is a motif
		of a stripe of $\ptext \in \Perm{n}$ if and only if there exist an increasing function $\phi : [|\pmotif|] \rightarrow [|\pmotif|]$
		such that : \\
		$\forall i \in [|\pmotif|]$, $\mathcal{S}(\pmotif,i) = \mathcal{S}(\ptext,\phi(i))$\\
		If a stripe $R_2$ is a motif of a stripe $R_1$,
		it means that there exists
		a subsequence of $R_1$ such as
		this sequence is equal to $R_2$.
%		We say that a set is a match 
%		if and only if there exists a function such as define above
%		and the set is the set of image of this function.\\
		For example, the stripe $(\dstep_1,\dstep_2,\dstep_3,\dstep_4,\ustep_1,\ustep_2)$ is a motif of  the stripe \\
		$(\dstep_1,\dstep_2,\dstep_3,\ustep_1,\ustep_2,\ustep_3,\ustep_4,\dstep_4,\dstep_5,\ustep_5,\ustep_6,\ustep_7)$ ,
		because we can match \\
		$(\dstep_1,\dstep_2,\dstep_3,\dstep_4)$ to $(\dstep_1,\dstep_2,\dstep_3,\dstep_4)$ and $(\ustep_1,\ustep_2)$ to 
		$(\ustep_5,\ustep_6)$.
		\begin{figure}[h!]
			\begin{displaymath}
				\xymatrix@=0.3cm{
					\dstep_1 \ar[dd] & \dstep_2 \ar[dd] & \dstep_3 \ar[dd] & \dstep_4\ar[ddrrrr]  & \ustep_1 \ar[ddrrrrr]& \ustep_2 \ar[ddrrrrr]  \\
					\\
					\dstep_1 & \dstep_2 & \dstep_3 & \ustep_1 & \ustep_2 & \ustep_3 & \ustep_4 & \dstep_4 & \dstep_5 & \ustep_5 & \ustep_6 & \ustep_7 & \\
				}
			\end{displaymath}     
		\end{figure}		
		But the stripe $(\dstep,\ustep,\dstep,\dstep,\dstep)$ is not a motif of the stripe\\ $(\dstep_1,\dstep_2,\dstep_3,\ustep_1,\ustep_2,\ustep_3,\ustep_4,\dstep_4,\dstep_5,\ustep_5,\ustep_6,\ustep_7)$.\\

		A \textbf{bivincular motif} generalize
		a motif. 
		A bivincular motif allows 
		to force element to be adjacent in position
		or/and in value.
		A bivincular motif
		is a motif with two set $\bmotif$,
		the first set contains the first index 
		of two consecutive index
		and the second set contains the first index
		of the two consecutive elements.
		Formally, Let $\bmotif$ 
		be a bivincular motif 
		and $\ptext$ a permutation.
		if $i \in \x$,
		and $i$ is matched with $j$ in $\ptext$
		then $i+1$ must be matched with $j+1$,
		with the special case of $0$ and $|\pmotif|$ :
		$0 \in \x$ then the first element of $\pmotif$
		must be matched with the first element of $\ptext$,
		and $|\pmotif| \in \x$ then the last element of $\pmotif$
		must be matched with the last element of $\ptext$.
		if $i \in \y$,
		and $i$ is matched with $j$ in $\ptext$
		then $i+1$ must be matched with $l$
		such as $\ptext(l)=\ptext(j)+1$,
		with the special case of $0$ and $|\pmotif|$ :
		$0 \in \y$ then the minimal element of $\pmotif$
		must be matched with the minimal element of $\ptext$,
		and $|\pmotif| \in \y$ then the maximal element of $\pmotif$
		must be matched with the maximal element of $\ptext$.

@@

		\textbf{Lemma  \numl{firstelement} \thenum} If a permutation is in $\C{n}$ 
		then the first element is either
		the minimal or the maximal element.\\

@@

		\textbf{Corollary  \num \thenum} A permutation $p \in \Perm{n}$ is in $\C{n}$ if and only if for $1 \leq i \leq n$ 
		$p[i:]$ start either with the maximal element
		or the minimal element of $p[i:]$.\\

		\textbf{Corollary \numl{stripe} \thenum}  If $p \in \C{n}$ its stripe can be define such as, \\
		$\mathcal{S}(p,i) = \left\{ 
  		\begin{array}{l l}
   			\ustep & \quad \text{if $p(i)$ is the minimal element of $p[i:]$}\\    
   			\dstep & \quad \text{if $p(i)$ is the maximal element of $p[i:]$}\\
  		 	\mathcal{S}(p,n-1) & \quad \text{if $i=n$}\\
	 	\end{array} \right. 
	 	$\\

		\textbf{Lemma \numl{updown}  \thenum} Let $p \in \C{n}$,
		$\forall i,j \in [n]$, 
		$i<j$, 
		$\mathcal{S}(p,i)=\ustep$
		and $\mathcal{S}(p,j)=\dstep$
		then $p(i)<p(j)$.\\

@@

		\textbf{Proof} By induction on the size of the permutation :
		the proposition is true for the permutations $(1,2)$ and $(2,1)$.
		Suppose the proposition true for $\C{n}$.
		Let $p \in \C{n+1}$, 
		we show that the proposition holds for $p$.
		Let $p'$ be the permutation $p[2:]$.
		$p' \in \C{n}$, so
		every element of $p'$ verify our lemma (by induction).
		We still need to compare the first element with the rest.
		Except that the first element
		is the maximal (minimal) element of all the permutation 
		(by Lemma \ref{firstelement}).
		Moreover if the first element is the maximal (minimal)
		it will mapped to an down step (up step).
		So the proposition is also true
		for the first element.
		$\Box$\\

		\textbf{Lemma \numl{upup} \thenum} Let $p \in \C{n}$,
		$\forall i,j \in [n]$, 
		$i<j$, 
		$\mathcal{S}(p,i)=\ustep$
		and $\mathcal{S}(p,j)=\ustep$
		then $p(i)<p(j)$.\\

@@

		\textbf{Lemma \numl{downdown} \thenum}  Let $p \in \C{n}$,
		$\forall i,j \in [n]$,
		$i<j$,
		$\mathcal{S}(p,i)=\dstep$
		and $\mathcal{S}(p,j)=\dstep$
		then $p(i)>p(j)$.\\

@@

		\textbf{Proposition \numl{patternMatchingStripe} \thenum} Let $\ptext, \pmotif \in \C{n}$.
		$\pmotif$ is a motif of $\ptext$ if and only if the stripe of $\pmotif$ is a motif of the stripe of $\ptext$.\\

		\textbf{Proof} \\
		$\Rightarrow$ Suppose that $\pmotif$ is a motif of $\ptext$
		by subsequence $s$.
		By definition $s$ normalized is equal to
		$\pmotif$ so they have the same stripe.\\ 
		$\Leftarrow$ 
		Let $\ptext \in \Perm{n}$, 
		$R_1$ be is stripe, 
		$\pmotif \in \Perm{m}$
		and $R_2$ is stripe.
		Let $\phi$ be the function
		that match $R_2$ to $R_1$.
		We define $\varphi$ as, 
		$\forall x \in [m]$,
		$\varphi(x) = \phi(x)$.
		Suppose\\ $\exists x,y \in [|\pmotif|], \text{ $\pmotif(x)<\pmotif(y)$ 
		and $\ptext(\varphi(x))>\ptext(\varphi(y))$ }$,
		without lost of generality we can suppose that $x<y$
		But :
		\begin{itemize}

			\item if $\pmotif(x)<\pmotif(y)$, 
			$\mathcal{S}(\pmotif,x)=\ustep$ 
			and $\mathcal{S}(\pmotif,y)=\ustep$
			(if x and y are increasing in $\pmotif$),
			then $\mathcal{S}(\ptext,\varphi(x))=\ustep$ and $\mathcal{S}(\ptext,\varphi(y))=\ustep$,
			(the match are also increasing).
			As $x<y$ and as $\varphi$ is an increasing function, 
			so $\varphi(x) < \varphi(y)$.
			And thus, by \textbf{Lemma \ref{upup}},
			$\ptext(\varphi(x)) < \ptext(\varphi(y))$ .
			which contradict our hypothesis,
			so this case is not possible.

			\item if $\pmotif(x)<\pmotif(y)$, 
			$\mathcal{S}(\pmotif,x)=\ustep$ 
			and $\mathcal{S}(\pmotif,y)=\dstep$
			then $\mathcal{S}(\ptext,\varphi(x))=\ustep$ and $\mathcal{S}(\ptext,\varphi(y))=\dstep$,
			As $x<y$ and as $\varphi$ is an increasing function, 
			so $\varphi(x) < \varphi(y)$.
			And thus, by \textbf{Lemma \ref{updown}},
			$\ptext(\varphi(x)) < \ptext(\varphi(y))$ .
			which contradict our hypothesis,
			so this case is not possible.

			\item if $\pmotif(x)>\pmotif(y)$, 
			$\mathcal{S}(\pmotif,x)=\dstep$ 
			and $\mathcal{S}(\pmotif,y)=\dstep$
			then $\mathcal{S}(\ptext,\varphi(x))=\dstep$ and $\mathcal{S}(\ptext,\varphi(y))=\dstep$,
			As $x<y$ and as $\varphi$ is an increasing function, 
			so $\varphi(y) < \varphi(x)$.
			And thus, by \textbf{Lemma \ref{downdown}},
			$\ptext(\varphi(y)) > \ptext(\varphi(x))$ .
			which contradict our hypothesis,
			so this case is not possible.

			\item if $\pmotif(x)>\pmotif(y)$, 
			$\mathcal{S}(\pmotif,x)=\dstep$ 
			and $\mathcal{S}(\pmotif,y)=\ustep$
			then $\mathcal{S}(\ptext,\varphi(x))=\dstep$ and $\mathcal{S}(\ptext,\varphi(y))=\ustep$,
			As $x<y$ and as $\varphi$ is an increasing function, 
			so $\varphi(y) < \varphi(x)$.
			And thus, by \textbf{Lemma \ref{updown}},
			$\ptext(\varphi(y)) > \ptext(\varphi(x))$ .
			which contradict our hypothesis,
			so this case is not possible.$\Box$

		\end{itemize}
		So this is not possible. $\Box$\\

@@

		\textbf{Proof}	
		To solve the permutation pattern for a permutation in $\C{n}$, 
		we find a match in the stripe of the permutation and the pattern.
		This can be done linearly by a greedy algorithm, 
		by matching a step whenever it is possible.
		And thank to the definition of the definition of a stripe in \textbf{Corollary \ref{stripe}},
		we do not have to compute the stripe advance.
		Therefore we have an (online) algorithm.$\Box$\\

@@

			For the algorithm we introduce a decomposition,
			we decompose the motif into
			adjacent element of same step in the stripe 
			(called such sequence segment),
			and label them form left to right
			with increasing number.
			Let's call this decomposition $S$.
			For each segment, we call important 
			the leftmost element denoted by $IMP$.
			For example, given the motif $(12,11,10,1,2,3,4,9,8,5,6,7)$,
			$S(1)=(5,6,7)$, $IMP(1)=5$, 
			$S(2)=(9,8)$, $IMP(2)=9$, 
			$S(3)=(1,2,3,4)$, $IMP(3)=1$, 
			$S(4)=(12,11,10)$ and $IMP(4)=12$.\\

			Given a up step (down step) segment $S(s)$,
			if we want to match 
			$\pmotif[IMP(s):]$
			with $\ptext[i:]$
			and match $IMP(s)$
			with $i$.
			The optimal way
			of matching
			$\pmotif[IMP(s-1):]$
			is to choose the
			minimal (maximal) element $\ptext(e)$
			such that :
			(1) $\pmotif[IMP(s-1):]$ is matched with $\ptext[e:]$
			and $IMP(s-1)$ is matched with $e$.
			(2) The segment $S(s)$ is matched with $\ptext[i:e-1]$
			and $IMP(s)$ is matched with $i$.
			(3) Every elements of the match of (2),
			is inferior to the minimal (maximal) element of the match of (1).
			In other word if we want to
			match the suffix $s_ns_{s-1}...s_1$
			starting with an up step (down step),
			and given that we know every
			match of $s_{s-1}...s_1$,
			the optimal way of matching
			$s_{s-1}...s_1$
			is to choose the match
			that minimize (maximize)
			the maximal (minimal)
			element of the match
			and that allow a match
			of $s_n$.
			Indeed when we will 
			match $s_{n+1}s_ns_{s-1}...s_1$
			more element will be available,
			because every matched 
			element of $s_{n+1}$
			must be superior (inferior)
			to every matched element
			of $s_{s-1}...s_1$.\\

>>>>

% 231,213
\newcommand{\myPattern}{231,231}

% avoid set
\DeclareMathOperator{\Avd}{Av}
\newcommand\Av[2]{\Avd_{{#1}}({#2})}

@@

\title{Pattern matching for (231,213) avoiding permutations}
\author{Both Emerite NEOU, Romeo RIZZI}
\date{}

@@

	\abstract{
	  	Given two permutations, 
	  	a text $\ptext$ 
	  	and a motif $\pmotif$,
	  	the \textbf{permutation pattern problem}
	  	asks if there exists a normalized subsequence of $\ptext$
	  	which equals $\pmotif$.
	  	We study this problem for the permutation 
	  	avoiding (231,231).
	}

@@

		We denote by $\Av{n}{213,231}$ the class
		of permutation of size $n$ which avoid 
		the motif $213$ and $231$. 
		$\Perm{n}$ the permutation of size $n$.
		$[n]$ the set $\{1,2,...,n\}.$
		For a permutation p, let $p[i:j]$, 
		be the permutation from element $i$ to $j$,
		$p[:j]$ be the prefix ending at index $j$
		and $p[i:]$ be the suffix starting at index $i$.\\

		Given two permutations
		$\pmotif$ and $\ptext$,
		we say that $\pmotif$
		is a motif/match of
		$\ptext$,
		if and only if
		there exists 
		and increasing function 
		$\sigma:[|\pmotif|] \rightarrow [|\pmotif|]$
		such that : $\forall i$ and 
		$\forall j$ $i,j \in |\pmotif| $
		if $\pmotif(i)<\pmotif(j)$
		then $\ptext(\sigma(i))<\ptext(\sigma(j))$.\\

@@

		A \textbf{Stripe} of a permutation
		 is a mapping into \textbf{up step} (noted $\ustep$) 
		or a \textbf{down step} (noted $\dstep$).
		An element $i$ of a permutation $p$ is an up step if and only if $i$ is not the last element and $p(i)<p(i+1)$.
		An element $i$ of a permutation $p$ is a down step if and only if $i$ is not the last element and $p(i)>p(i+1)$.	
		By convention the last element is mapped as the second to last element.\\ 	
		Formally a Stripe is a function $\mathcal{S} : [n] \to \{\dstep,\ustep\}$ define as :\\
		$ \mathcal{S}(p,i) = \left\{ 
		  \begin{array}{l l}
		    \ustep & \quad \text{if $1 \leq i<n$ and $p(i+1)-p(i)>0$ }\\
		    \dstep & \quad \text{if $1 \leq i<n$ and $p(i+1)-p(i)<0$ }\\
		     \mathcal{S}(p,n-1) & \quad \text{if $i=n$}\\
		  \end{array} \right. $\\

@@

		Formally we say that the stripe of $\pmotif \in \Perm{m}$ is a motif
		of a stripe of $\ptext \in \Perm{n}$ if and only if there exist an increasing function $\phi : [|\pmotif|] \rightarrow [|\pmotif|]$
		such that : \\
		$\forall i \in [|\pmotif|]$, $\mathcal{S}(\pmotif,i) = \mathcal{S}(\ptext,\phi(i))$\\
		If a stripe $R_2$ is a motif of a stripe $R_1$,
		it means that there exists
		a subsequence of $R_1$ such as
		this sequence is equal to $R_2$.
%		We say that a set is a match 
%		if and only if there exists a function such as define above
%		and the set is the set of image of this function.\\
		For example, the stripe $(\dstep_1,\dstep_2,\dstep_3,\dstep_4,\ustep_1,\ustep_2)$ is a motif of  the stripe \\
		$(\dstep_1,\dstep_2,\dstep_3,\ustep_1,\ustep_2,\ustep_3,\ustep_4,\dstep_4,\dstep_5,\ustep_5,\ustep_6,\ustep_7)$ ,
		because we can match \\
		$(\dstep_1,\dstep_2,\dstep_3,\dstep_4,(\ustep_1,\ustep_2)$ to $(\dstep_1,\dstep_2,\dstep_3,\dstep_4,\ustep_5,\ustep_6)$.
		\begin{figure}[h!]
			\begin{displaymath}
				\xymatrix@=0.3cm{
					\dstep_1 \ar[dd] & \dstep_2 \ar[dd] & \dstep_3 \ar[dd] & \dstep_4\ar[ddrrrr]  & \ustep_1 \ar[ddrrrrr]& \ustep_2 \ar[ddrrrrr]  \\
					\\
					\dstep_1 & \dstep_2 & \dstep_3 & \ustep_1 & \ustep_2 & \ustep_3 & \ustep_4 & \dstep_4 & \dstep_5 & \ustep_5 & \ustep_6 & \ustep_7 & \\
				}
			\end{displaymath}     
		\end{figure}		
		But the stripe $(\dstep,\ustep,\dstep,\dstep,\dstep)$ is not a motif of the stripe\\ $(\dstep_1,\dstep_2,\dstep_3,\ustep_1,\ustep_2,\ustep_3,\ustep_4,\dstep_4,\dstep_5,\ustep_5,\ustep_6,\ustep_7)$.\\

		A \textbf{bivincular motif} generalize
		a motif. 
		A bivincular motif allows 
		to force element to be adjacent in position
		or/and in value.
		A bivincular motif
		is a motif with two set $\bmotif$,
		the first set contains the first index 
		of two consecutive indexes
		and the second set contains the first indexes
		of the two consecutive elements.
		Formally, Let $\bmotif$ 
		be a bivincular motif 
		and $\ptext$ a permutation.
		if $i \in \x$,
		and $i$ is matched with $j$ in $\ptext$
		then $i+1$ must be matched with $j+1$,
		with the special case of $0$ and $|\pmotif|$ :
		if $0 \in \x$ then the first element of $\pmotif$
		must be matched with the first element of $\ptext$,
		and if $|\pmotif| \in \x$ then the last element of $\pmotif$
		must be matched with the last element of $\ptext$.
		if $i \in \y$,
		and $i$ is matched with $j$ in $\ptext$
		then $i+1$ must be matched with $l$
		such as $\ptext(l)=\ptext(j)+1$,
		with the special case of $0$ and $|\pmotif|$ :
		if $0 \in \y$ then the minimal element of $\pmotif$
		must be matched with the minimal element of $\ptext$,
		and if $|\pmotif| \in \y$ then the maximal element of $\pmotif$
		must be matched with the maximal element of $\ptext$.

@@

		\textbf{Lemma  \numl{firstelement} \thenum} If a permutation is in $\Av{n}{}$ 
		then the first element is either
		the minimal or the maximal element.\\

@@

		\textbf{Corollary  \num \thenum} A permutation $p \in \Perm{n}$ is in $\Av{n}{213,231}$ if and only if for $1 \leq i \leq n$, 
		$p[i:]$ start either with the maximal element
		or the minimal element of $p[i:]$.\\

		\textbf{Corollary \numl{stripe} \thenum}  If $p \in \Av{n}{213,231}$ its stripe can be define such as, \\
		$\mathcal{S}(p,i) = \left\{ 
  		\begin{array}{l l}
   			\ustep & \quad \text{if $p(i)$ is the minimal element of $p[i:]$}\\    
   			\dstep & \quad \text{if $p(i)$ is the maximal element of $p[i:]$}\\
  		 	\mathcal{S}(p,n-1) & \quad \text{if $i=n$}\\
	 	\end{array} \right. 
	 	$\\

		\textbf{Lemma \numl{updown}  \thenum} Let $p \in \Av{n}{213,231}$,
		$\forall i,j \in [n]$, 
		$i<j$, 
		if $\mathcal{S}(p,i)=\ustep$
		and $\mathcal{S}(p,j)=\dstep$
		then $p(i)<p(j)$.\\

@@

		\textbf{Proof} By induction on the size of the permutation :
		the proposition is true for the permutations $(1,2)$ and $(2,1)$.
		Suppose the proposition true for $\Av{n}{213,231}$.
		Let $p \in \Av{n}{213,231}$, 
		we show that the proposition holds for $p$.
		Let $p'$ be the permutation $p[2:]$.
		$p' \in \Av{n}{213,231}$, so
		every element of $p'$ verify our lemma (by induction).
		We still need to compare the first element with the rest.
		But the first element
		is the maximal (minimal) element of all the permutation 
		(by Lemma \ref{firstelement}).
		Moreover if the first element is the maximal (minimal)
		it will mapped to an down step (up step).
		So the proposition is also true
		for the first element.
		$\Box$\\

		\textbf{Lemma \numl{upup} \thenum} Let $p \in \Av{n}{213,231}$,
		$\forall i,j \in [n]$, 
		$i<j$, 
		if $\mathcal{S}(p,i)=\ustep$
		and $\mathcal{S}(p,j)=\ustep$
		then $p(i)<p(j)$.\\

@@

		\textbf{Lemma \numl{downdown} \thenum}  Let $p \in \Av{n}{213,231}$,
		$\forall i,j \in [n]$,
		$i<j$,
		if $\mathcal{S}(p,i)=\dstep$
		and $\mathcal{S}(p,j)=\dstep$
		then $p(i)>p(j)$.\\

@@

		\textbf{Proposition \numl{patternMatchingStripe} \thenum} Let $\ptext, \pmotif \in \Av{n}{213,231}$.
		$\pmotif$ is a motif of $\ptext$ if and only if the stripe of $\pmotif$ is a motif of the stripe of $\ptext$.\\

		\textbf{Proof} \\
		$\Rightarrow$ Suppose that $\pmotif$ is a motif of $\ptext$
		by subsequence $s$.
		By definition $s$ normalized is equal to
		$\pmotif$ so they have the same stripe.\\ 
		$\Leftarrow$ 
		Let $\ptext \in \Perm{n}$, 
		$R_1$ be its stripe, 
		$\pmotif \in \Perm{m}$
		and $R_2$ its stripe.
		Let $\phi$ be the function
		that match $R_2$ to $R_1$.
		We define $\varphi$ as, 
		$\forall x \in [m]$,
		$\varphi(x) = \phi(x)$.
		Suppose that $\exists x,y \in [|\pmotif|]$, 
		$\pmotif(x)<\pmotif(y)$ 
		and $\ptext(\varphi(x))>\ptext(\varphi(y))$,
		without lost of generality we can suppose that $x<y$,
		Let see all the case possible that can make this 
		hypothesis possible :
		\begin{itemize}

			\item if $\pmotif(x)<\pmotif(y)$, 
			$\mathcal{S}(\pmotif,x)=\ustep$ 
			and $\mathcal{S}(\pmotif,y)=\ustep$
			(if x and y are increasing in $\pmotif$),
			then $\mathcal{S}(\ptext,\varphi(x))=\ustep$ and $\mathcal{S}(\ptext,\varphi(y))=\ustep$,
			(the match are also increasing).
			As $x<y$ and as $\varphi$ is an increasing function, 
			$\varphi(x) < \varphi(y)$.
			And thus, by \textbf{Lemma \ref{upup}},
			$\ptext(\varphi(x)) < \ptext(\varphi(y))$ .
			Which contradict our hypothesis,
			so this case is not possible.

			\item if $\pmotif(x)<\pmotif(y)$, 
			$\mathcal{S}(\pmotif,x)=\ustep$ 
			and $\mathcal{S}(\pmotif,y)=\dstep$
			then $\mathcal{S}(\ptext,\varphi(x))=\ustep$ and $\mathcal{S}(\ptext,\varphi(y))=\dstep$,
			As $x<y$ and as $\varphi$ is an increasing function, 
			$\varphi(x) < \varphi(y)$.
			And thus, by \textbf{Lemma \ref{updown}},
			$\ptext(\varphi(x)) < \ptext(\varphi(y))$ .
			Which contradict our hypothesis,
			so this case is not possible.

			\item if $\pmotif(x)>\pmotif(y)$, 
			$\mathcal{S}(\pmotif,x)=\dstep$ 
			and $\mathcal{S}(\pmotif,y)=\dstep$
			then $\mathcal{S}(\ptext,\varphi(x))=\dstep$ and $\mathcal{S}(\ptext,\varphi(y))=\dstep$,
			As $x<y$ and as $\varphi$ is an increasing function, 
			$\varphi(y) < \varphi(x)$.
			And thus, by \textbf{Lemma \ref{downdown}},
			$\ptext(\varphi(y)) > \ptext(\varphi(x))$ .
			Which contradict our hypothesis,
			so this case is not possible.

			\item if $\pmotif(x)>\pmotif(y)$, 
			$\mathcal{S}(\pmotif,x)=\dstep$ 
			and $\mathcal{S}(\pmotif,y)=\ustep$
			then $\mathcal{S}(\ptext,\varphi(x))=\dstep$ and $\mathcal{S}(\ptext,\varphi(y))=\ustep$,
			As $x<y$ and as $\varphi$ is an increasing function, 
			$\varphi(y) < \varphi(x)$.
			And thus, by \textbf{Lemma \ref{updown}},
			$\ptext(\varphi(y)) > \ptext(\varphi(x))$ .
			Which contradict our hypothesis,
			so this case is not possible.$\Box$

		\end{itemize}
		So our hypothesis is not realisable.So our assertion is true. $\Box$\\

@@

		\textbf{Proof}	
		To solve the permutation pattern for a permutation in $\Av{n}{213,231}$, 
		we find a find a match of the stripe of the pattern in the stripe of the text.
		This can be done linearly by a greedy algorithm, 
		by matching a step whenever it is possible.
		And thank to the definition of the definition of a stripe in \textbf{Corollary \ref{stripe}},
		we do not have to compute the stripe advance.
		Therefore we have an linear (online) algorithm.$\Box$\\

@@

			For the algorithm we introduce a decomposition,
			we decompose the motif into
			adjacent element of same step in the stripe 
			(called such sequence segment),
			and label them form right to left
			with increasing number.
			Let's call this decomposition $S$.
			For each segment, we call important 
			the leftmost element denoted by $IMP$.
			For example, given the motif $(12,11,10,1,2,3,4,9,8,5,6,7)$,
			$S(1)=(5,6,7)$, $IMP(1)=5$, 
			$S(2)=(9,8)$, $IMP(2)=9$, 
			$S(3)=(1,2,3,4)$, $IMP(3)=1$, 
			$S(4)=(12,11,10)$ and $IMP(4)=12$.\\

			Given a up step (down step) segment $S(s)$,
			if we want to
			match the suffix $s_ns_{s-1}...s_1$
			starting with an up step (down step),
			and given that we know every
			match of $s_{s-1}...s_1$,
			the optimal way of matching
			$s_{s-1}...s_1$
			is to choose the match
			that minimize (maximize)
			the maximal (minimal)
			element of the match
			and that allow a match
			of $s_n$.			
			In other word if we want to match 
			$\pmotif[IMP(s):]$
			with $\ptext[i:]$
			and match $IMP(s)$
			with $i$.
			The optimal way
			of matching
			$\pmotif[IMP(s-1):]$
			is to choose the
			minimal (maximal) element $\ptext(i')$
			such that :
			(1) $\pmotif[IMP(s-1):]$ is matched with $\ptext[i':]$
			and $IMP(s-1)$ is matched with $e$.
			(2) The segment $S(s)$ is matched with $\ptext[i:i'-1]$
			and $IMP(s)$ is matched with $i$.
			(3) Every elements of the match of (2),
			is inferior (superior) to the minimal (maximal) element of the match of (1).
			Indeed when we will 
			match $s_{n+1}s_ns_{s-1}...s_1$
			more element will be available,
			because every matched 
			element of $s_{n+1}$
			must be superior (inferior)
			to every matched element
			of $s_{s-1}...s_1$.\\
